### 2020-01-21 README.Rmd
Update manuscript title in README

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and GTPases. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins and GTPases". 
version x.x.x. Zenodo. URL.

>>>>

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2019) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins". 
version x.x.x. Zenodo. URL.
